{\bf Practical Concurrency Testing}

### 2018-10-17 thesis/defense/snakefight.tex
snakefight last draft

\begin{frame}{Setting}
	%CMU (15-410, S'15-S'18), PSU (CMPSC 473, S'18)
	CMU (15-410), PSU (CMPSC 473)
	\begin{itemize}
		\item Thread library (``P2'')
			\begin{itemize}
				\item POSIX-like userspace thread library %(also teams of 2)
				\item Implement {\tt thr\_create()}/{\tt exit()}/{\tt join()}, {\tt mutex\_lock()}, etc.
				\item Reference ``Pebbles'' kernel provided
					% say: later they implement this in p3
				%\item Fixed APIs $\rightarrow$ instrumentation can be automated
				%\item Still needs heuristics to handle ad-hoc synchronization
			\end{itemize}
		\item Kernel (``P3'') - reimplement said reference kernel (CMU only)
	\end{itemize}
	\pause
	\linegap

@@

	Bug-finding
	\begin{itemize}
		\item CMU: 115 deterministic, 122 concurrency bugs in 75/103 P2s
		\item U. Chicago: 3 deterministic, 4 concurrency bugs in 3/4 kernels
		\item PSU: (no log collection) %due to IRB issues)
		% \item Case study tej
	\end{itemize}
\end{frame}

@@

	%...as well as subsequent P3 (kernel) grades
	...as well as subsequent kernel grades
	\begin{itemize}
		\item ``Does Landslide teach students lasting lessons about concurrency?''
	\end{itemize}
\end{frame}

@@

	\hilight{gray}{stateless model checking}\xspace
	\hilight{sect-pastel-quicksand}{can sufficiently mitigate exponential explosion}\xspace
	\hilight{sect-pastel-410}{to be practical for inexperienced users}\xspace
	\hilight{sect-pastel-htm}{and real-world programs alike.}\xspace
\end{frame}
\begin{frame}{Conclusion}
	%\hilight{gray}{Combining %both
	%{\bf theoretically-founded automatic reduction techniques}}
	Combining %both
	{\bf theoretically-founded automatic reduction techniques}
	\begin{itemize}
		\item \hilight{sect-quicksand}{Verification with data-race preemption points}
		\item \hilight{sect-410}{Student yield-loop blocking} % student (adj). from "studence"
		\item \hilight{sect-htm}{Equivalent emulation of HTM semantics}
	\end{itemize}
	%\hilight{gray}{and {\bf user-informed heuristic ones},}
	and {\bf user-informed heuristic ones},
	\begin{itemize}
		\item \hilight{sect-quicksand}{Quicksand's CPU budget argument}
		\item \hilight{sect-410}{Exposing data-race reports to students}
		%\item Encouraging students to exercise their intuition % ??
		\item \hilight{sect-htm}{Abstraction reduction for HTM primitives}
	\end{itemize}
	\linegap

>>>>

\begin{frame}{Setting}
	%CMU (15-410, S'15-S'18), PSU (CMPSC 473, S'18)
	CMU (15-410), PSU (CMPSC 473)
	\begin{itemize}
		\item Thread library (``P2'')
			\begin{itemize}
				\item POSIX-like userspace thread library %(also teams of 2)
				\item Implement {\tt thr\_create()}/{\tt exit()}/{\tt join()}, {\tt mutex\_lock()}, etc.
				\item Reference ``Pebbles'' kernel provided, later reimplemented
					% say: later they implement this in p3
				%\item Fixed APIs $\rightarrow$ instrumentation can be automated
				%\item Still needs heuristics to handle ad-hoc synchronization
			\end{itemize}
		%\item Kernel (``P3'') - reimplement said reference kernel (CMU only)
	\end{itemize}
	\pause
	\linegap

@@

	Bug-finding
	\begin{itemize}
		\item CMU: %115 deterministic,
			122 concurrency bugs in 75/103 P2s
		\item U. Chicago: %3 deterministic,
			4 concurrency bugs in 3/4 kernels
		\item PSU: (no log collection) %due to IRB issues)
		% \item Case study tej
	\end{itemize}
\end{frame}

@@

	%%...as well as subsequent P3 (kernel) grades
	%...as well as subsequent kernel grades
	%\begin{itemize}
	%	\item ``Does Landslide teach students lasting lessons about concurrency?''
	%\end{itemize}
\end{frame}

\begin{frame}{Effect on Grades (CMU)}
	\begin{center}
		\includegraphics[width=\textwidth]{photo-of-ze-studence-box-p2-only.pdf}
	\end{center}
\end{frame}
\begin{frame}{Effect on Grades (CMU)} % - statistically significant?}
	\begin{center}
		\includegraphics[width=\textwidth]{photo-of-ze-studence-cdf-p2-only-no-pre-study.pdf}
	\end{center}
\end{frame}
\begin{frame}{Effect on Grades (CMU)} % - statistically significant?}
	\begin{center}
		\includegraphics[width=\textwidth]{photo-of-ze-studence-cdf-p2-only.pdf}
	\end{center}
\end{frame}

@@

	\hilight{gray}{stateless model checking}\xspace
	\hilight{sect-pastel-quicksand}{can sufficiently mitigate exponential explosion}\xspace
	\hilight{sect-pastel-410}{to be practical for inexperienced users}\xspace
	\hilight{sect-pastel-htm}{and real-world programs alike.}\xspace
\end{frame}
\begin{frame}{Conclusion}
	%\hilight{gray}{Combining %both
	%{\bf theoretically-founded automatic reduction techniques}}
	Combining %both
	{\bf theoretically-founded automatic reduction techniques}
	\begin{itemize}
		\item \hilight{sect-quicksand}{Verification with data-race preemption points}
		\item \hilight{sect-410}{Student yield-loop blocking} % student (adj). from "studence"
		\item \hilight{sect-htm}{Equivalent emulation of HTM semantics}
	\end{itemize}
	%\hilight{gray}{and {\bf user-informed heuristic ones},}
	and {\bf user-informed heuristic ones},
	\begin{itemize}
		\item \hilight{sect-quicksand}{Prioritizing jobs based on fixed CPU budget}
		\item \hilight{sect-410}{Exposing data-race reports to students}
		%\item Encouraging students to exercise their intuition % ??
		\item \hilight{sect-htm}{Abstraction reduction for HTM primitives}
	\end{itemize}
	\linegap
